Next Trippy Structures\thanks{Supported by organization x.}

### 2019-03-07 paper.tex
Complete appendix

We demonstrate the main advantage of \ctr~over the older \ttctr~ in the Figure~\ref{fig:start}b, where restricting a line or a time interval for an \texttt{end\_X} query is prohibitively expensive for \ttctr~ due to its separate vocabulary for final stops, requiring to query the \texttt{CSA} for every possible stop that could have been boarded before X to restrict a line. In the Figure~\ref{fig:start}a it is also possible to see how the performance of \ctr~degrades less with a highly compressed \texttt{CSA} for the query \texttt{start\_X$_T$}, where even queries over a compressed \texttt{WML} are faster than queries over the \texttt{CSA}.

@@

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/start.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/end.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{start\_X$_{LT}$} (a) and \texttt{end\_X$_{LT}$} (b) queries, with all variants. Note that the logarithmic scale for the y axis in (b)}
\label{fig:start}
\end{figure}

>>>>

We demonstrate the main advantage of \ctr~over the older \ttctr~ in the Figure~\ref{fig:start}b, where restricting a line or a time interval for an \texttt{end\_X} query is very expensive for \ttctr~ due to its separate vocabulary for final stops, requiring to query the \texttt{CSA} for every possible stop that could have been boarded before X to restrict a line. In the Figure~\ref{fig:start}a it is also possible to see how the performance of \ctr~degrades less with a highly compressed \texttt{CSA} for the query \texttt{start\_X$_T$}, where even queries over a compressed \texttt{WML} are faster than queries over the \texttt{CSA}.

@@

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/start.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/end.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{start\_X$_{LT}$} (a) and \texttt{end\_X$_{LT}$} (b) queries, with all variants. Note the logarithmic scale for the y axis in (b)}
\label{fig:start}
\end{figure}
